%============ Projects ============%
\section*{Selected Projects}

\begin{itemize}[leftmargin=12pt]
    \item \textbf{ari64} — C big integer library focused mainly on cryptographic implementations and arbitrary-precision arithmetic.
    \item \textbf{RetailBase.Identity} — Authentication and user management module with secure registration, recovery, and JWT-based enterprise auth flows.
    \item \textbf{RetailBase} — Modular enterprise foundation with reusable backend building blocks and layered architecture.
    \item \textbf{diagrams} — Lightweight HTML-based project for publishing technical and architectural diagrams.
    \item \textbf{HookHubNet} — Secure TCP tunneling over WebSockets with centralized hub and dynamic port forwarding.
    \item \textbf{Cryoinfra Platforms} — Web and mobile systems (.NET Core, .NET MAUI) for logistics, production monitoring, and internal operations.
    \item \textbf{Cryoinfra Architecture} — Defined layered architecture, service contracts, and development standards.
    \item \textbf{Help Desk System} — Internal ticketing platform with AI-assisted support (Watson AI).
    \item \textbf{Hard.Core} — Modular enterprise framework accelerating application development.
    \item \textbf{Private CI/CD} — Self-hosted pipelines using Jenkins, Docker, and Ansible.
    \item \textbf{HookHub} — Real-time messaging hub using ASP.NET Core and SignalR.
    \item \textbf{Midori64 / Midori128} — Lightweight cryptographic block cipher implementations.
\end{itemize}
