%============ Academic Activities & Honors ============%
\section*{Academic Activities, Conferences \& Honors}

\subsection{International Conferences}
\begin{itemize}[leftmargin=12pt]
    \item \textbf{LatinCrypt 2017} — Fifth International Conference on Cryptology and Information Security in Latin America.  
    University of Havana, Cuba (Sept. 2017).  
    Certificate of Participation.
\end{itemize}

\subsection{Research Presentations}
\begin{itemize}[leftmargin=12pt]
    \item \textit{“Analysis of an Embedded Web Interface on an Arduino Platform and a Custom-Built Device.”}  
    3rd Research Conference of the Systems Department, Universidad Autónoma Metropolitana (July 2014).
\end{itemize}

\subsection{Programming Competitions \& Honors}
\begin{itemize}[leftmargin=12pt]
    \item \textbf{ACM-ICPC Mexico \& Central America Regional Contest} — Honorable Mention  
    ITESM (2013).
    \item \textbf{ACM-ICPC Mexico \& Central America Regional Contest} — Honorable Mention  
    ITESM (2012).
    \item \textbf{ACM-ICPC Mexico \& Central America Regional Contest} — Honorable Mention  
    ITESM (2011).
    \item \textbf{IV Annual Programming Contest “Dennis M. Ritchie”} — Second Place  
    IPN–ESCOM (2012).
\end{itemize}

\subsection{ACM Competitive Programming Training}
\begin{itemize}[leftmargin=12pt]
    \item ACM Student Chapter — ITESM Mexico City (2011)
    \item ACM Student Chapter — BUAP Puebla (2012)
    \item ACM Student Chapter — ESCOM-IPN Mexico City (2013)
\end{itemize}
