%============ Experience ============%
\section*{Professional Experience}

\subsection*{Independent Contractor \hfill 2025 to Present}
\begin{itemize}[leftmargin=12pt]
    \item Deliver software engineering and infrastructure services for custom business systems, internal platforms, and technical enablement initiatives.
    \item Developed and maintained recent independent projects including \textit{RetailBase}, \textit{RetailBase.Identity}, \textit{poc-vite-crud}, \textit{hard.core.web}, \textit{HookHubNet}, \textit{ScepServer}, and \textit{ari64}.
    \item Managed and configured VPS environments, VPN connectivity, mail servers, collaboration platforms, and CI/CD tooling, including provisioning, hardening, deployment automation, backups, SSL/TLS, and operational support.
    \item Use a Spec-Driven development pipeline assisted end-to-end with GitHub Copilot, covering requirement discovery, analysis, specification design, refinement, solution building, testing, deployment, monitoring, and maintenance.
\end{itemize}

\subsection*{Software Developer / Technical Leader \hfill Cryoinfra — 2019 to 2025}
\begin{itemize}[leftmargin=12pt]
    \item Led multidisciplinary SCRUM-based teams, ensuring timely delivery of high-impact software solutions.
    \item Designed, implemented, and maintained a microservices-based architecture secured with JWT authentication.
    \item Integrated AI tools into daily engineering work to accelerate bug fixing, refactoring, test generation, technical documentation, and implementation analysis, while keeping human validation and engineering quality gates in place.
    \item I started exploring \textit{vibe coding} patterns in recent projects to iterate quickly, but the more reliable approach I found was a Spec-Driven workflow: defining requirements, contracts, acceptance criteria, and implementation tasks first. That approach is reflected especially in ScepServer, HookHubNet, hard.core.web, and poc-vite-crud.
    \item Developed scalable web and mobile applications using Razor Pages, .NET Core, and .NET MAUI.
    \item Integrated and orchestrated multiple internal and external APIs for data synchronization across systems.
    \item Defined technical documentation standards, including architecture diagrams, workflows, and coding guidelines.
    \item Mentored junior developers, conducted code reviews, and promoted best practices in software development.
    \item Provided user support and technical training for internal tools and enterprise applications.
\end{itemize}

\subsection*{Laboratory Academic \hfill Universidad Autónoma Metropolitana - Azcapotzalco — 2014 to 2017}
\begin{itemize}[leftmargin=12pt]
    \item Developed and maintained departmental web site and applications using PHP, JavaScript, and MySQL.
    \item Administered Linux and Windows servers, as well as departmental network infrastructure.
    \item Maintained and supported Systems Department classrooms and laboratories.
    \item Contributed to teaching and research activities by assisting faculty and supporting academic projects.
\end{itemize}

\subsection*{Junior Software Developer \hfill Cryoinfra — 2012 to 2014}
\begin{itemize}[leftmargin=12pt]
    \item Developed monolithic web and desktop applications using .NET Framework and SQL Server.
    \item Collaborated closely with QA and product teams to ensure high-quality deliverables.
    \item Diagnosed and resolved complex issues in third-party components (e.g., Telerik).
    \item Optimized database queries, improving application performance and reliability.
    \item Provided help desk and technical support for internal users.
\end{itemize}
